### 2016-03-22 paper.tex
Add information about the design experiment.

\textit{Paco will describe the team that undertook the design challenge, including the articulation of our three goals and the design elements being used to realize them}

>>>>

Our experiment involved a team of eleven undergraduate students and one mentor.
The students who participated came from a variety of disciplines, including
programming, writing, social research, and art.  The project included 
a lot of unique tasks, so each person also contributed with their own unique 
skills.  Each student who participated registered under three credit hours.  
For two hours every Monday, Wednesday, and Friday, the team met to
discuss the project and work on development together.

At the beginning of the semester, the team started discussing their goals for
the semester.  Before creating any game concepts, we discussed what our goals
should be for the project and ended up with three:

\begin{enumerate}

\item \textit{A technology component.}  During our first discussions,
we mentioned having designs that had both digital and physical components, or
even designs that were purely physical (such as \totan).
We decided that it was important to us that whatever we develop contain at least
some digital component.  As we hashed out the concept of game we wanted to
create, it ended up being completely digital.

\item \textit{Cultural empathy.} Beyond adhering to the principles of culture-
narration games, we wanted to create something that taught children
about other cultures and why it's important to value other cultures.
Originally, we described this as \textit{cultural literacy}, but quickly
realized as we continued researching for our game that this already had some
meaning that wasn't exactly what we were looking for.

\item \textit{Narrative as the driving force.} Culture-narration games tell
stories, and it was important to us that our game tell stories.  Doing this in
a way that was interesting and processable for children proved to be one of the 
biggest challenges.

After these goals were defined, the team figured out a game concept, and 
developed it throughout three iterations.
The deadlines for each iteration provided the team a chance to reflect on both
the project itself and on our methodology.  Each iteration was tested at
\textit{the library branch}, providing valuable data for which directions we
should bring the project.  We also had reflective meetings in which we 
discussed what worked about our methodology, and what should change.  During
the first two iterations, we organized our tasks using \textit{story mapping}.
However, we realized during our second reflective meeting that it might be
better to switch to Scrum.

We used JavaFX for rough prototyping, which some of the developers had used
before, and then moved to \textit{PlayN}, a cross-platform library that allowed
us to build both for Java and HTML.
Our writers and artist continually developed and improved assets for the game,
learning how to bring them into the game easily.  The writers also developed a
methodology for workshopping each other to make sure the narrative was 
developed and had a consistent voice.

Most of the team played vital roles in both the research side of the game and
the development side of the game.  The writers, for example, did extensive
research on different cultures and monsters as well as writing in a way that
would be easy for kids to read.  Writers and developers were involved in the
playtesting as well, and gained valuable insight on what the kids needed and
wanted.

We also invited guests to join us during our regular meeting times to talk about
their experiences with games, monsters, and children's literacy.  One of our
guests gave us valuable insight on what monsters mean to people and how they are
influenced by culture.
